---
title: "Ocean Acidification Monitoring Gaps and Hotspots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Identifying Ocean Acidification Monitoring Gaps and Hotspots in the California Current System

Ocean Acidification (OA) is progressing on the West Coast of North America at a rate 2x higher than the global average. However, with enhanced monitoring and evaluation, marine managers can be better prepared to understand how OA is changing regionally, and creating effects locally.

## West Coast Ocean Acidification and Hypoxia (OAH) Monitoring Inventory
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(leaflet)
oahfocus <- read_csv("oahfocus.csv")

leaflet(oahfocus) %>%
      addProviderTiles('Esri.OceanBasemap') %>% 
      addCircleMarkers(
        radius = 6, 
        weight=7,
        color = "black",
        popup = paste("Project ID: ", oahfocus$ProjectID, "<br>",
                      "Organization: ", oahfocus$Orgnztion, "<br>"),
          
        stroke=FALSE, fillOpacity = 1)
  
```


