---
title: "Ocean Acidification Hotspot and MPA Analysis"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1. Create Predicted Aragonite Saturation State Surfaced via Kriging
#### Load packages
```{r load packages, message = FALSE, warning = FALSE}

if (!require(pacman)) install.packages("pacman")
library(pacman)
p_load(
  tidyverse, here, 
  sp, rgdal, gstat, tibble, fields, leaflet, tmap,sf, dplyr, raster, 
  mapview)

```

####Prepare cruise data set
```{r data wrangling, message = FALSE, warning = FALSE}

aragonite_data <- read_csv(here("data/WCOAC_2013_test.csv")) #load data
colnames(aragonite_data) <- c("Date", "Time", "Lat", "Long", "Pressure", "OmegaAr") #rename columns in dataframe

aragonite_data <- aragonite_data %>% #remove N/A values
  mutate(OmegaAr=replace(OmegaAr, OmegaAr==-999.000, NA)) %>%
  na.omit(aragonite_data)

aragonite_data<- aragonite_data[aragonite_data[, 5]<5,] #filter for surface observations

coordinates(aragonite_data)<-  ~ Long + Lat #transform into spatial points

zd<-zerodist(aragonite_data)
aragonite_data<-aragonite_data[-zd[,2],] #remove observations taken at same coordinate point

```

####Interpolation via simple kriging
```{r interpolation, message = FALSE, warning = FALSE, results = 'hide'}

aragonite_var<-variogram(OmegaAr ~1, data=aragonite_data, alpha=c(0, 45, 90, 135))
plot(aragonite_var) #look for anisotropy and create variogram of aragonite values

aragonite_fit<-fit.variogram(aragonite_var,model=vgm(nugget=0.2,psill=1,range=2,model="Exp", anis=c(0, 0.3))) #fit a model to the values based on estimated nugget, sill, and range, and anisotropy
plot(aragonite_var,aragonite_fit)

extent <- bbox(aragonite_data) #get extent of cruise observations 
long<-seq(extent[1,1],extent[1,2],length=388) #increase ROI by one degree in each direction
lat<-seq(extent[2,1],extent[2,2],length=1000)

aragonite_grid<-expand.grid(long,lat) #create grid for interpolation surface
colnames(aragonite_grid)<- c("long", "lat")
coordinates(aragonite_grid) <- ~ long + lat
gridded(aragonite_grid)=TRUE

aragonitekrige<-krige(OmegaAr ~ 1, aragonite_data, newdata=aragonite_grid, model=aragonite_fit) #run kriging on interpolation grid, based on best fit model

```

####Create continuous raster
```{r raster, message = FALSE, warning = FALSE}

aragonite_raster<-raster(aragonitekrige, layer=1, values=TRUE) #transform krige object to raster
projection(aragonite_raster) <- CRS("+proj=longlat +datum=WGS84") #set CRS 
aragonite_raster_proj <- projectRaster(aragonite_raster, crs=CRS('+init=EPSG:6414'),method="ngb") #re-project to California Teale Albers Equal Area

```

##Part 2. Create hotspot thresholds mask 
```{r hotspots, message = FALSE, warning = FALSE}

thresholds <- c(0,1,1, 1,1.7,1.7, 1.7,2,2, 2,10,NA)
thresholdsmatrix <- matrix(thresholds, ncol=3, byrow=TRUE)
hotspotmask <- reclassify(aragonite_raster_proj, thresholdsmatrix)

```

##Part 3. Compare predicted aragonite saturation state and hotspots to MPA Location
####Load shapefiles
```{r shapefiles, message = FALSE, warning = FALSE, results = 'hide'}

poly_MPA <- readOGR(dsn=path.expand("/Users/courtneycochran/downloads/all_mpas_update"), layer="all_mpas_update") #Load MPA shapefile using pathway on personal computer

poly_MPA <- spTransform(poly_MPA, crs(aragonite_raster_proj)) #Assign same CRS as aragonite layer

poly_coast<- readOGR(dsn=path.expand("/Users/courtneycochran/downloads/Export_Output_2"), layer="Export_Output_2") #Load coast shapefile using pathway on personal computer

poly_coast <- spTransform(poly_coast, crs(aragonite_raster_proj)) #Assign same CRS as aragonite layer

estuary <- readOGR(dsn=path.expand("/Users/courtneycochran/Downloads/estuaries"), layer="estuaries") #Load estuary shapefile using pathway on personal computer

estuary <- spTransform(estuary, crs(aragonite_raster_proj)) #Assign same CRS as aragonite layer

Canada <- readOGR(dsn=path.expand("/Users/courtneycochran/Downloads/Canada"), layer="Canada") #Load Canada shapefile using pathway on personal computer 

Canada <- spTransform(Canada, crs(aragonite_raster_proj)) #Assign same CRS as aragonite layer 
```

####Clip rasters to coast
```{r clipping, message = FALSE, warning = FALSE}

aragonite_clipped <- mask(aragonite_raster_proj, poly_coast, inverse = TRUE) #Clip continuous raster
aragonite_clipped <- mask(aragonite_clipped, estuary, inverse = TRUE) #Clip raster layer to exclude estuaries
aragonite_clipped <- mask(aragonite_clipped, Canada, inverse = TRUE) #Clip raster layer to Canada layer


hotspot_clipped <- mask(hotspotmask, poly_coast, inverse = TRUE) #Clip hotspot mask to the coast
hostspot_clipped <- mask(hotspot_clipped, estuary, inverse = TRUE) #Clip hotspot layer to exclude estuaries
hotspot_clipped <- mask(hotspot_clipped, Canada, inverse = TRUE) #Clip hotspot layer to Canada layer

```

####Zonal statistics - mean saturation state
```{r mean saturation state, message = FALSE, warning = FALSE}

aragonite_mean<- raster::extract(aragonite_clipped, poly_MPA, fun=mean, na.rm=TRUE, df=TRUE) #Calculate mean aragonite saturation state of each MPA from continuous aragonite layer and export as dataframe
colnames(aragonite_mean) <- c("OBJECTID", "ARAGONITE_MEAN") #Create column names for new dataframe

poly_MPA@data[,1] <- seq(1, length(poly_MPA@data[,1])) #Replace "OBJECTID" with sequenced list to remove duplicates and change from factor to integer form
poly_MPA@data <- poly_MPA@data %>% 
  left_join(aragonite_mean, by = 'OBJECTID') #Merge dataframes to add mean aragonite saturation state to poly_MPA dataframe

```

####Zonal statistics - percent cover of hotspot
```{r percent hotspot cover, message = FALSE, warning = FALSE}

pctcover <- raster::extract(hotspot_clipped, poly_MPA, fun=function(x, ...) length(na.omit(x))/length(x), df=TRUE) #Calculate percentage of total MPA area covered by threshold of concern
colnames(pctcover) <- c("OBJECTID", "PCT_HOTSPOTCOVER")

poly_MPA@data <- poly_MPA@data %>% 
  left_join(pctcover, by = 'OBJECTID') #Merge dataframes to add the percentage of MPA covered by a hotspot to MPA dataframe

```

##Part 4. Visualizing Aragonite Saturation, Hotspots and MPA Zonal Statistics
```{r}
pal <- colorRampPalette(c("red", "white", "royalblue2")) 
pal2 <- colorRampPalette(c("red", "darkorange1", "gold")) #Color palettes used for maps

tmap_mode("view")


tm_shape(aragonite_clipped) +
  tm_raster(palette = pal(3),  breaks = seq(0.8,3, by=0.2),
             title="Aragonite Saturation State") + 
  tm_layout(basemaps = c('OpenStreetMap')) #Map of aragonite saturation state layer, showing range of values from 0.8 to 3 by 0.2 increments 


tm_shape(hotspot_clipped) +
  tm_raster(hotspot_clipped, breaks= c(0, 1.1, 1.8, 2.1),
            palette = pal2(2), title="Aragonite Saturation State") +
  tm_layout(basemaps=c('OpenStreetMap')) #Map of hotspots, displays the three thresholds displayed by our group of less than 2, less than 1.7 and less than 1 


tm_shape(poly_MPA) + tm_polygons("ARAGONITE_MEAN", palette=pal(3), colorNA=NULL,
                                 breaks=seq(.8,3, by=0.2),
                                 title="Mean Aragonite \nSaturation State") +
  tm_layout(basemaps = c('OpenStreetMap')) #Map of MPAs with their fill corresponding to the mean aragonite saturation state within their boundaries


tm_shape(poly_MPA) + tm_polygons("PCT_HOTSPOTCOVER", palette=pal(7),
                                 breaks=seq(0, 1, by=0.1),
                                 title="Percent of MPA Covered by Hotspot") +
  tm_layout(basemaps=c('OpenStreetMap')) #Map of MPAs with their fill corresponding to the percent of the MPA covered by a hotspot


```

